\bf Visual Inference for Significance and Goodness-of-Fit Testing for a Social Network Model

### 2017-10-30 ASApaper/paper-child.Rnw
commit changes from earlier in the day

Using the ``Picking Lineups" web application, we settled on six parameter values to test for each of our six effects, $\beta_1, \dots \beta_6$. The complete details of the parameters tested using the lineup protocol is given in Table~\ref{tab:experdetail}. In the case of both $\beta_4$ and $\beta_6$, we could not determine a value for negative effects that made the data simulated from M3 and M5 look different than null model simulations from model M1. Because we could not detect these effects at these values, we decided that the less experienced participants in our experiment would also not be able to. So instead of testing the negative values of these effects, we examined a different scenario: we placed 5 simulations from positive values of the parameter with one simulation from model M1 in a lineup. We did this to determine if the perception of the effect size would be symmetric: if an effect is noticed $x$\% of the time at value $\beta_k = \beta_{k_0}$ when one simulation from the corresponding model is placed among five null plots from model M1, then when five simulations from the model with $\beta_k = \beta_{k_0}$ are put in a lineup with one simulation from model M1, the plot from the simpler model should be noticed about $x$\% of the time as well.

@@

>>>>

Using the ``Picking Lineups" web application, we settled on six parameter values to test for each of our six effects, $\beta_1, \dots \beta_6$. The complete details of the parameters tested using the lineup protocol is given in Table~\ref{tab:experdetail}. In the case of both $\beta_4$ and $\beta_6$, we could not determine a value for negative effects that made the data simulated from M3 and M5 look different than null model simulations from model M1. Because we could not detect these effects at these values, we decided that the less experienced participants in our experiment would also not be able to. So instead of testing the negative values of these effects, we examined a different scenario: we placed 5 simulations from positive values of the parameter with one simulation from model M1 in a lineup. We refer to this later on as the ``reverse" scenario. We used the reverse scenario to determine if the perception of the effect size would be symmetric: if an effect is noticed $x$\% of the time at value $\beta_k = \beta_{k_0}$ when one simulation from the corresponding model is placed among five null plots from model M1, then when five simulations from the model with $\beta_k = \beta_{k_0}$ are put in a lineup with one simulation from model M1, the plot from the simpler model should be noticed about $x$\% of the time as well.

@@

All of the parameters we test for significance using the lineup protocol, $\beta_3$ and $\beta_4$, were determined to be statistically significant using Equation~\ref{eq:wald1}. The results from the significance tests we performed using the lineup protocol are given in Table~\ref{tab:sigtesting}

<<sigtesting, results='asis'>>=
turk22_sig <- turk22 %>% 
  mutate(type2 = ifelse(sign == 0, sign(initialEst), sign),
         type2 = ifelse(type == "one", type2, -1)) %>% 
  filter(param_value == 1)
summ_sig <- turk22_sig %>% group_by(pic_id, test_param) %>% 
  summarize(npick = sum(datapick), n = n(), 
            pv = map2_dbl(npick, n, pV, m=6, scenario=3))
names(summ_sig) <- c("Lineup ID", "parameter", "# Alt. Model Picks", "Total Views", "p-value")
summ_sig$parameter <- as.factor(summ_sig$parameter)
levels(summ_sig$parameter) <- c("beta3", "beta4")
print(xtable::xtable(summ_sig, caption = "Experiment results for the two parameters for which we performed significance tests. There were three lineups for each parameter, so there are three results for each plot.", label = "tab:sigtesting", digits = c(0,0,0,0,0,5)), include.rownames = FALSE)
@
